Untrusted B2B Collaboration using the Blockchain

### 2018-07-09 paper/paper.tex
Add notes for related work section

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%
\author{Jonas Beyer \and
Philipp Otto\and
S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut, Potsdam, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle % typeset the header of the contribution
%
\begin{abstract}
Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
This allows for consensus in communication between otherwise untrusting parties.
In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.

\keywords{Blockchain \and Business Processes \and Ethereum \and Choreography \and Smart Contract \and BPMN}
\end{abstract}
%
%
%
\section{Introduction}

@@

\subsection{Orchestrations and Choreographies}
A work by Weber et. al \citep{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations. They use a smart contract that all parties of a business process communicate with.

@@

\subsection{Prior Work on Business Processes on the Blockchain}
%summarize untrusted paper
%summarize Caterpillar
%acknowledge their Work
%display the shortcomings

>>>>

\documentclass[runningheads]{llncs}

\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Untrusted B2B Collaboration using the Blockchain}
%
%
\author{Jonas Beyer \and Philipp Otto \and S\"oren Tietb\"ohl}
%
\authorrunning{J. Beyer et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Hasso-Plattner-Institut, Potsdam, Germany\\
\email{\{jonas.beyer,philipp.otto2,soeren.tietboehl\}@student.hpi.de}}
%
\maketitle % typeset the header of the contribution
%
\begin{abstract}
Lack of trust between communication partners is one of the major issues companies face when implementing business processes in a cross-organizational setting.
Blockchain is an emerging technology that enables decentralization and distribution of state without the need for a trusted central instance.
As a result, it is possible to form consensus in the communication between otherwise untrusting parties.
In this paper we introduce Armadillo, an open-source prototype implementation for realizing business process choreographies using the Ethereum blockchain.
We present a user interface for connecting business processes with blockchain calls, as well as an underlying smart contract structure for inter-process communication.

\keywords{Business Processes \and BPMN \and Choreographies \and Blockchain \and Ethereum \and Smart Contracts}
\end{abstract}
%
%
%
\section{Introduction}

@@

\subsection{Orchestrations and Choreographies}
A work by Weber et al. \cite{weber2016untrusted} showed how to use the blockchain to monitor and coordinate business processes across organizations.
They use a smart contract that all parties of a business process communicate with.

@@

\subsection{Prior Work on Business Processes on the Blockchain}
%summarize untrusted paper
In \cite{weber2016untrusted}, a first approach of monitoring business process interactions on the blockchain was presented.
Using a smart contract as a central \it{monitor} or \it{mediator} of the communication, a form of inter-process orchestration is implemented.

we build on:
factories \& instances
registering users to roles
triggers
the model they used (originally from Fdhila et al)

we don\'t:
do bpmn solidity translation
use one central contract instance

%summarize Caterpillar
\cite{lopez2017caterpillar} presents an open-source implementation of an Ethereum-based process engine.

describes components and architecture of engine
automatic bpmn solidity translation
no choreographies / lanes supported, all tasks / transitions are managed on-chain through process contract
